Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2021-06-14 analysis/paper/paper.Rmd
deletes an errant space
Revise CSV to ODS

Each journal was classified as to whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
The five-year impact factor for 2018 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
This was downloaded, saved as a CSV file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package [@Wickham2020] for analysis when the `import_notes()` command is executed.

>>>>

Each journal was classified as to whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
The five-year impact factor for 2018 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
This was downloaded, saved as an Open Document Spreadsheet (ODS) file and is left-joined with the article notes using a `left_join()` from the 'dplyr' package [@Wickham2020] for analysis when the `import_notes()` command is executed.
